Rapid and Accurate Global PTM Discovery (G-PTM-D) Using Post-Acquisition Spectral Calibration and Multi-Notch Searches

### 2017-07-12 paper.tex
coisolation

>>>>

[Cite Bo Zhang if paper exists].
We showed above in some amazing figure an example where several peptides were co-eluting from the column into that mass-spec within the tolerance used for isolation for fragmentation.
In that particular case, the precursor with m/z dsfadf was chosen for isolation and fragmentation.
In a conventional search, only that precursor mass would be used to select a range of theoretical for comparison.
However, all peptides in that range are co-fragmented and a better solution would be to use all co-isolated precursor masses.
In MetaMorpheus, for each MS2 scan, the corresponding MS1 scan is deconvoluted and the complete list of precursors is gathered for the range surrounding the isolated precursor (+/- 3 Da).
Each deconvoluted mass is used to select a range of theoreticals to use for identification.
The result of this is that often, more than one peptide can be identified from a single MS2 scan.
Below, in Table 3434, we should the number of PSMs for a raw file where we use only a single precursor mass and we compare that to the case where we allow for multiple different precursors.
You can see a significant increase in the number of identified PSMs.
Importantly, you can see in Supplemental Figure erf3e, that the precursor mass errors go down significantly and the standard deviation is much reduced.
This is extremely benficial in both open mass and multi-notch searches because it reduces the number the more difficult to interpret mass shifts and substantially improves G-PTM-D (see below).

Get the story about how precurors with similar m/z with different z can in their deconvoluted state be many (10s, 100s of Da apart).
This is a big problem in general searches but also for open mass and multi-notch searches which are used to discover possible PTMs.
